\vspace{-15mm}\fontsize{16pt}{10pt}\selectfont\textbf{Facial Expression Recognition with\\ Convolutional Neural Networks}

### 2018-04-17 doc/paper.tex
face detection

Automatically recognizing facial expressions is an interesting and challenging problem in the fields human computer interaction and artificial emotional intelligence. Facial expressions can be interpreted and categorized into six classes of basic emotion that seem to be found across all human cultures: anger, disgust, fear, happiness, sadness, and surprise \cite{ekman93}. This projects goal is to develop a classifier for real-time detection of these facial expressions.

@@

In simple CNNs, it is common to combine convolutional and pooling layers to compute feature activations while reducing dimensionality. During the designing process, it turned out that stacking multiple convolutional layers in a VGG-Fashion \cite{simonyan14} improved the model accuracy on the test set by about 20 percent compared to alternating pooling and convolutional layers.

@@

%\begin{thebibliography}{9}
%
%	% OpenCV Haarcascade Classifier
%	\bibitem{violajones}
%  	P. A. Viola and M. J. Jones. Robust real-time face detection.
%	International Journal of Computer Vision
%	57(2):137–154, 2004.
%
%	% the ICML 2013 workshop’s facial expression recognition challenge
%	\bibitem{replearning}
%	I. J. Goodfellow et al.
%	Challenges in representation learning: A report on three machine
%	learning contests.
%	Neural Networks
%	, 64:59 – 63, 2015.
%	Special Issue on ‘Deep Learning of Representations’
%	
%	%[LeCun and Bengio, 1995a]
%    %Y. LeCun and Y. Bengio. Convolutional networks for images, speech, and time-series. 
%    %In M. A. Arbib, 		editor, The Handbook of Brain Theory and Neural Networks. MIT Press, 1995
%    
%    % Paul Ekmans 1969 research paper "Facial Expressions"
%
% 
%\end{thebibliography}

>>>>

Automatically recognizing facial expressions is an interesting and challenging problem in the fields human computer interaction and artificial emotional intelligence. Facial expressions can be interpreted and categorized into six classes of basic emotion that seem to be found across all human cultures: anger, disgust, fear, happiness, sadness, and surprise \cite{ekman93}. This projects goal is to develop a classifier for real-time detection of these facial expressions. To simplify the process and focus on the main problem, faces are being detected using the OpenCV Haar feature-based cascade classifier \cite{violajones04}.

@@

In simple CNNs, it is common to combine convolutional and pooling layers to compute feature activations while reducing dimensionality. During the designing process, it turned out that stacking multiple convolutional layers in improved the model accuracy on the test set by about 20 percent compared to alternating pooling and convolutional layers.

@@

%\begin{thebibliography}{9}
%
%	% OpenCV Haarcascade Classifier

%
%	% the ICML 2013 workshop’s facial expression recognition challenge
%	\bibitem{replearning}
%	I. J. Goodfellow et al.
%	Challenges in representation learning: A report on three machine
%	learning contests.
%	Neural Networks
%	, 64:59 – 63, 2015.
%	Special Issue on ‘Deep Learning of Representations’
%	
%	%[LeCun and Bengio, 1995a]
%    %Y. LeCun and Y. Bengio. Convolutional networks for images, speech, and time-series. 
%    %In M. A. Arbib, 		editor, The Handbook of Brain Theory and Neural Networks. MIT Press, 1995
%    
%    % Paul Ekmans 1969 research paper "Facial Expressions"
%
% 
%\end{thebibliography}
